Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Merge

\begin{abstract}
This work describes an investigation on the structural optimization of the crash response of aircraft or road vehicle crash boxes, where the force pulse due to frontal impact or hard landing wanted to be kept as stable as possible while reducing the mass of the energy absorbing systems. The objective functions are minimized in a multi-objective approach using metamodeling on FE models and genetic evolutionary algorithms. Finite element models were subjected to loading conditions simulating, for example, an impact test against a simplified rigid wall in the case of the car model, or a hardlanding impact for the fuselage model. Force-displacement curves were obtained from the analysis and suitably filtered. The objective was to obtain a force-time curve which was as close as possible to the ideal dissipator curve, with lower values of the peaks of acceleration experienced by the occupants; and to minimize the mass for fuel saving and environmental reasons. To that end, optimization strategies were planned carefully to deal with problems which are typical in crashworthiness optimization like expensive computation times and numerical noise.
\end{abstract}\\
\emph{Keywords: crashworthiness, damage reduction, size optimization, surrogate models.}

@@

The tube is crushed between two rigid plates, one fixed and the other moving at impact speed (see \Cref{fig:general}). In order to ease the formation of a stable collapse mechanism, a triggering is machined near the front end of the tube. The trigger starts a desired collapse mode in that area. Due to the high slenderness of the tube, difficulties were found in order to achieve stable collapse mechanisms. On their place, tubes diverted from their axis. Trying to avoid these critical situations, four rigid plates on a rectangular section around the crash tube were added to the model as a bounding box. Its section was $\num{100}\times\SI{60}{\mm}$ and co-centered with the crash box.

>>>>

\begin{abstract}
This work describes an investigation on the structural optimization of the crash response of aircraft or road vehicle crash boxes, where the force pulse due to frontal impact or hard landing wanted to be kept as stable as possible while reducing the mass of the energy absorbing systems. The objective functions are minimized in a multi-objective approach using metamodeling on finite element models and genetic evolutionary algorithms. Finite element models were subjected to loading conditions simulating, for example, an impact test against a simplified rigid wall in the case of the car model, or a hardlanding impact for the fuselage model. Force-displacement curves were obtained from the analysis and suitably filtered. The objective was to obtain a force-time curve which was as close as possible to the ideal dissipator curve, with lower values of the peaks of acceleration experienced by the occupants; and to minimize the mass for fuel saving and environmental reasons. To that end, optimization strategies were planned carefully to deal with problems which are typical in crashworthiness optimization like expensive computation times and numerical noise.
\end{abstract}\\
\emph{Keywords: crashworthiness, damage reduction, size optimization, surrogate models.}

@@

The tube is crushed between two rigid plates, one fixed and the other moving at impact speed (see \Cref{fig:general}). In order to ease the formation of a stable collapse mechanism, a triggering is machined near the front end of the tube. Due to the high slenderness of the tube, difficulties were found in order to achieve stable collapse mechanisms. On their place, tubes diverted from their axis. Trying to avoid these critical situations, four rigid plates on a rectangular section around the crash tube were added to the model as a bounding box. Its section was $\num{100}\times\SI{60}{\mm}$ and co-centered with the crash box.
